Modeling Intervention Strategies for United States TB Control

### 2014-02-08 in_progress/presentations/paper/draft.tex
Appendix
style things

\section{Appendix}
\subsection{Hill Constants}
Below, we detail some of the relevant constants in the Basic Hill Model, and their best-fit
values. A full listing of constants used in the original Hill Model can be found in <CITATION HERE> 
\begin{figure}[h]
  \begin{center}
    \tiny{
    \begin{verbatim}
sigmaLBase  <- 0.057
fBase       <- 0.187
transBase   <- 1
incLTBIBase <- 1

#Treatment Effectiveness Data:
probHosp      <- .49 #Probability of hospitalization for active TB treatment
efficacyLTBI  <- .9  #LTBI treatement efficacy
adherenceLTBI <- .64 #LTBI treatment adherence
probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI

#Cost Parameter Values: 
costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
costLTBI <- 403.45 #LTBI treatment cost
Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment

parms <- c(
mu0   = 1/78,      #Natural mortality rate USB per year
mu1   = 1/53,      #Natural mortality rate FB per year
ro    = 0.018,     #USB birth rate per year
alpha = 0.005,     #FB arrival rate per year
p     = 0.103,     #Fraction of new infections which are acute (fast
progressors)
vF    = 1.5,       #Progression rate of acute infection per year
l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB
population per year
vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB
population per year
q     = 0.708,     #Fraction of infections progressing to infectious disease
mud   = 0.115,     #Mortality rate due to TB per year
x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute
infection
ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
beta  = 10.39,     #Effective contact rate per year
e0    = 0.965,     #Fraction of preferred contacts with own population for USB
e1    = 0.985,     #Fraction of preferred contacts with own population for FB
g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active
disease for both populations pre year RATES (USB)
phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active
disease for both populations pre year RATES (FB)
sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for
both populations per year RATES (USB)
sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for
both populations per year RATES (FB)
sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
fBase = fBase,      #Fraction of FB arrivals with LTBI

#2010 New Cases in Population i (millions)
#source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
newCases0 = .008714,  #US-born
newCases1 = .007554,  #Foreign-born

CtBase = Ct,
ClBase = Cl
)
    \end{verbatim}
  }
  \end{center}
  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
  \label{fig:basicHillConstants}
\end{figure}
\subsection{The Extended Hill Equations}
Below, we detail the full equations used in the extended hill model. These
equations extend those used in the standard Hill Model. In many cases, the
equations of the Hill model were split into their component parts, which could
then be tracked separately. 
\begin{figure}[h]
  \begin{center}
  \tiny{
    \begin{verbatim}
discV   <- 1/(1.03^t)  #amount costs, health states discount constant

#parameter values initialized for each time step
c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
dprogTotalD1 <- discV * dprogTotal1                              #Progression to Active TB with discounting (FB)
lambda0      <- transmission*(beta*(c00*(I0/N0) + c01*(I1/N1)))  #Forces of Infection (USB)
lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))

#Difference Equations (USB)
dS0 <- ro*(N0+N1) + sigmaF0*F0 + sigmaL*L0 + phi0*(I0+J0) - lambda0*S0 - mu0*S0
dF0 <- p*lambda0*S0 + dexogenous0 - (mu0 + vF + sigmaF0)*F0
dL0 <- (1-p)*lambda0*S0 - dexogenous0 - (mu0 + vL0 + sigmaL)*L0
dI0 <- q*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*I0
dJ0 <- (1-q)*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*J0

#Difference Equations (FB)
dS1 <- (1-incLTBI)*dLTBIEn+(1-f)*alpha*(N0+N1) + sigmaF1*F1 + sigmaL*L1 + phi1*(I1 + J1) - lambda1*S1 - mu1*S1
dF1 <- g*p*dLTBIEn*incLTBI + p*lambda1*S1 + dexogenous1 - (mu1 + vF + sigmaF1)*F1
dL1 <- (1-g*p)*dLTBIEn*incLTBI + (1-p)*lambda1*S1 - dexogenous1 - (mu1 + vL1 +sigmaL)*L1
dI1 <- q*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*I1
dJ1 <- (1-q)*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*J1

dN0 <- dS0 + dF0 + dL0 + dI0 + dJ0
dN1 <- dS1 + dF1 + dL1 + dI1 + dJ1

#Cost calculations
dcL0 <- discV * Cl * sigmaL  * 1e6 * L0                    #cost for Chronic LTBI cures      (USB)
dcF0 <- discV * Cl * sigmaF0 * 1e6 * F0                    #cost for Acute LTBI cures        (USB)
dcI0 <- discV * Ct * q*(dprogAcute0 + dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
dcJ0 <- discV * Ct * (1-q)*(dprogAcute0 + dprogChron0) * 1e6 #cost for Non-Infectious TB cures (USB)
dcI0dL0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
dcI0dF0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
dcJ0dL0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
dcJ0dF0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
dcL1 <- discV * Cl * sigmaL  * 1e6 * L1                    #cost for Chronic LTBI cures      (FB)
dcF1 <- discV * Cl * sigmaF1 * 1e6 * F1                    #cost for Acute LTBI cures        (FB)
dcI1 <- discV * Ct * q*(dprogAcute1 + dprogChron1) * 1e6     #cost for Infectious TB cures     (FB)
dcJ1 <- discV * Ct * (1-q)*(dprogAcute1 + dprogChron1) * 1e6 #cost for Non-Infectious TB cures (FB)
dcI1dL1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
dcI1dF1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
dcJ1dL1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
dcJ1dF1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
dcN0 <- dcF0 + dcL0 + dcI0 + dcJ0                            #Total cost for all treatments (USB)
dcN1 <- dcF1 + dcL1 + dcI1 + dcJ1                            #Total cost for all treatments (FB)
    \end{verbatim}
  }
  \end{center}
  \label{fig:extendedHillEqs}
  \caption{
    The equations defining the Extended Hill Model, shown in \texttt{R} syntax.
    In this model, compartments share the same names as they did in the Hill
    Model, \emph{i.e.} \texttt{S1} is the Foreign Born susceptible population. 
  }
\end{figure}
Here, a continuous discounting approximation is used to a discount rate of $3\%$
yearly, found via $discV$. In many of the differential equations, a small $c$ is
used to denote \emph{cost of}. 
\FloatBarrier
\subsection{Estimations for Infectious Rates of FB and USB}

@@

\vspace{5mm}
{\bf Original Hill Model Parameters} 
(USB = US born, FB = Foriegn born)
\begin{enumerate}[1.] \itemsep 0em
\item{$\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)}
\item{$v^{L}_{0}$   = 0.0014 (Progression rate for reactivation in the USB population)}
\item{$v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)}
\item{$f$                = 0.187 (Fraction of FB arrivals with LTBI)}
\item{$p$               = 0.103 (Fraction of new infections which are acute)}
\item{$ARI_{0}$     = 0.00030 (2000 Annual Risk of Infection, USB)}
\item{$q$               = 0.708 (Fraction of infections progressing to infectious disease)}
\item{$g$               = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)}
\item{$\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)}
\item{$r_{0}$          = 0.667 (Fraction of cases due to reactivation in USB population)}
\item{$r_{1}$          = 0.780 (Fraction of cases due to reactivation in FB population)}
\item{$\mu^{d}$      = 0.115 (Mortality rate due to TB)}
\item{$x$                 = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)}
\item{$\phi$            = 0.897 (Cumulative fraction self-cure and treatment of active disease)}
\item{$e_{0}$          = 0.965 (Fraction of preferred contacts within own population for USB)}
\item{$e_{1}$          = 0.985 (Fraction of preferred contacts within own population for FB)}
\end{enumerate}
\vspace{2mm}
{\bf Additional Cost Parameters}
\begin{enumerate}[1.] \itemsep 0em
\item{$C_{A}$           = \$14,014.50 (Cost per Active TB treatment)}
\item{$C_{L}$           = \$700 (Cost per Latent TB treatment)}
\end{enumerate}
\vspace{5mm}

@@

To gain insight about strategies to reduce the cost burden for TB in the US, we
focus on the parameters with the greatest PRCC magnitudes for Total Cost aside
from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.  All these
parameters have PRCC magnitudes above 0.7, and are highly correlated with the
total cost burden of TB borne by the US projected over the next 100 years.  Out
of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of
Infection among the US born population in the year 2000, and therefore is
unchangeable under any intervention strategy.  The parameters $p$ (the fraction
of new infections which are acute) and $q$ (the fraction of infections
progressing to infectious disease) are variables which depend on physiological
disease dynamics, and may be altered with advances in medicine or mutations in
the bacterial strains of TB.  The parameter $f$ is the fraction of FB arrivals
with LTBI, which may vary depending on US immigration policies and medical
practices.  These results suggest that treating cases of LTBI among new FB
arrivals may be the most cost efficient intervention strategy to reduce the
disease burden for TB in the US, under the assumptions of the Hill model.  \\

\subsection{Stochastic Model}
\end{document}

>>>>

\section{Appendix}
\subsection{Hill Constants}
Below, we detail some of the relevant constants in the Basic Hill Model, and
their best-fit values. A full listing of constants used in the original Hill
Model can be found in <+CITATION HERE+>. 
%\begin{figure}[h]
%  \begin{center}
%    \tiny{
%    \begin{verbatim}
%sigmaLBase  <- 0.057
%fBase       <- 0.187
%transBase   <- 1
%incLTBIBase <- 1
%
%
%#Treatment Effectiveness Data:
%probHosp      <- .49 #Probability of hospitalization for active TB treatment
%efficacyLTBI  <- .9  #LTBI treatement efficacy
%adherenceLTBI <- .64 #LTBI treatment adherence
%probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI 
%
%#Cost Parameter Values: 
%costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
%costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
%costLTBI <- 403.45 #LTBI treatment cost
%Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
%Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment
%
%parms <- c(
%mu0   = 1/78,      #Natural mortality rate USB per year
%mu1   = 1/53,      #Natural mortality rate FB per year
%ro    = 0.018,     #USB birth rate per year
%alpha = 0.005,     #FB arrival rate per year
%p     = 0.103,     #Fraction of new infections which are acute (fast
%progressors)
%vF    = 1.5,       #Progression rate of acute infection per year
%l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
%l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
%r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
%r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
%vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB
%population per year
%vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB
%population per year
%q     = 0.708,     #Fraction of infections progressing to infectious disease
%mud   = 0.115,     #Mortality rate due to TB per year
%x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute
%infection
%ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
%beta  = 10.39,     #Effective contact rate per year
%e0    = 0.965,     #Fraction of preferred contacts with own population for USB
%e1    = 0.985,     #Fraction of preferred contacts with own population for FB
%g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
%phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active
%disease for both populations pre year RATES (USB)
%phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active
%disease for both populations pre year RATES (FB)
%sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for
%both populations per year RATES (USB)
%sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for
%both populations per year RATES (FB)
%sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
%fBase = fBase,      #Fraction of FB arrivals with LTBI
%
%#2010 New Cases in Population i (millions)
%#source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
%newCases0 = .008714,  #US-born
%newCases1 = .007554,  #Foreign-born
%
%CtBase = Ct,
%ClBase = Cl
%)
%    \end{verbatim}
%  }
%  \end{center}
%  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
%  \label{fig:basicHillConstants}
%\end{figure}
\subsection{The Extended Hill Equations}
Below, we detail the full equations used in the extended hill model. These
equations extend those used in the standard Hill Model. In many cases, the
equations of the Hill model were split into their component parts, which could
then be tracked separately. 
%\begin{figure}[h]
%  \begin{center}
%  \tiny{
%    \begin{verbatim}
%discV   <- 1/(1.03^t)  #amount costs, health states discount constant
%
%#parameter values initialized for each time step
%c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
%c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
%c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
%c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
%dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
%dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
%dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
%dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
%dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
%dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
%dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
%dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
%dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
%dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
%dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
%dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
%dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
%dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
%dprogTotalD1 <- discV * dprogTotal1                              #Progression to Active TB with discounting (FB)
%lambda0      <- transmission*(beta*(c00*(I0/N0) + c01*(I1/N1)))  #Forces of Infection (USB)
%lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
%dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
%dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
%dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))
%
%#Difference Equations (USB)
%dS0 <- ro*(N0+N1) + sigmaF0*F0 + sigmaL*L0 + phi0*(I0+J0) - lambda0*S0 - mu0*S0
%dF0 <- p*lambda0*S0 + dexogenous0 - (mu0 + vF + sigmaF0)*F0
%dL0 <- (1-p)*lambda0*S0 - dexogenous0 - (mu0 + vL0 + sigmaL)*L0
%dI0 <- q*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*I0
%dJ0 <- (1-q)*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*J0
%
%#Difference Equations (FB)
%dS1 <- (1-incLTBI)*dLTBIEn+(1-f)*alpha*(N0+N1) + sigmaF1*F1 + sigmaL*L1 + phi1*(I1 + J1) - lambda1*S1 - mu1*S1
%dF1 <- g*p*dLTBIEn*incLTBI + p*lambda1*S1 + dexogenous1 - (mu1 + vF + sigmaF1)*F1
%dL1 <- (1-g*p)*dLTBIEn*incLTBI + (1-p)*lambda1*S1 - dexogenous1 - (mu1 + vL1 +sigmaL)*L1
%dI1 <- q*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*I1
%dJ1 <- (1-q)*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*J1
%
%dN0 <- dS0 + dF0 + dL0 + dI0 + dJ0
%dN1 <- dS1 + dF1 + dL1 + dI1 + dJ1
%
%#Cost calculations
%dcL0 <- discV * Cl * sigmaL  * 1e6 * L0                    #cost for Chronic LTBI cures      (USB)
%dcF0 <- discV * Cl * sigmaF0 * 1e6 * F0                    #cost for Acute LTBI cures        (USB)
%dcI0 <- discV * Ct * q*(dprogAcute0 + dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
%dcJ0 <- discV * Ct * (1-q)*(dprogAcute0 + dprogChron0) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcI0dL0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
%dcI0dF0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
%dcJ0dL0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcJ0dF0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcL1 <- discV * Cl * sigmaL  * 1e6 * L1                    #cost for Chronic LTBI cures      (FB)
%dcF1 <- discV * Cl * sigmaF1 * 1e6 * F1                    #cost for Acute LTBI cures        (FB)
%dcI1 <- discV * Ct * q*(dprogAcute1 + dprogChron1) * 1e6     #cost for Infectious TB cures     (FB)
%dcJ1 <- discV * Ct * (1-q)*(dprogAcute1 + dprogChron1) * 1e6 #cost for Non-Infectious TB cures (FB)
%dcI1dL1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
%dcI1dF1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
%dcJ1dL1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcJ1dF1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcN0 <- dcF0 + dcL0 + dcI0 + dcJ0                            #Total cost for all treatments (USB)
%dcN1 <- dcF1 + dcL1 + dcI1 + dcJ1                            #Total cost for all treatments (FB)
%    \end{verbatim}
%  }
%  \end{center}
%  \label{fig:extendedHillEqs}
%  \caption{
%    The equations defining the Extended Hill Model, shown in \texttt{R} syntax.
%    In this model, compartments share the same names as they did in the Hill
%    Model, \emph{i.e.} \texttt{S1} is the Foreign Born susceptible population. 
%  }
%\end{figure}
Here, a continuous discounting approximation is used to a discount rate of $3\%$
yearly, found via $discV$. In many of the differential equations, a small $c$ is
used to denote \emph{cost of}. 
\FloatBarrier
\subsection{Estimations for Infectious Rates of FB and USB}

@@

\vspace{5mm}
{\bf Original Hill Model Parameters} 
(USB = US born, FB = Foriegn born)
%\begin{enumerate}[1.] \itemsep 0em
%  \item $\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)
%  \item $v^{L}_{0}$  = 0.0014 (Progression rate for reactivation in the USB population)
%  \item $v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)
%  \item $f$          = 0.187 (Fraction of FB arrivals with LTBI)
%  \item $p$          = 0.103 (Fraction of new infections which are acute)
%  \item $ARI_{0}$    = 0.00030 (2000 Annual Risk of Infection, USB)
%  \item $q$          = 0.708 (Fraction of infections progressing to infectious disease)
%  \item $g$          = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)
%  \item $\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)
%  \item $r_{0}$      = 0.667 (Fraction of cases due to reactivation in USB population)
%  \item $r_{1}$      = 0.780 (Fraction of cases due to reactivation in FB population)
%  \item $\mu^{d}$    = 0.115 (Mortality rate due to TB)
%  \item $x$          = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)
%  \item $\phi$       = 0.897 (Cumulative fraction self-cure and treatment of active disease)
%  \item $e_{0}$      = 0.965 (Fraction of preferred contacts within own population for USB)
%  \item $e_{1}$      = 0.985 (Fraction of preferred contacts within own population for FB)
%\end{enumerate}
%\vspace{2mm}
\begin{align*}
  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
                                 population)}\\
  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
                                 population)}\\
  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
                                 disease)}\\
  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
                                 progressors)}\\
  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
                                 infection)}\\
  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
                                 population)}\\
  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
                                 population)}\\
  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
                                 acute infection)}\\
  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
                                 active disease)}\\
  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
                                 population for USB)}\\
  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
                                population for FB)}\\
%\end{align*}
&\text{\bf Additional Cost Parameters}\\
%\begin{align*}
  C_{A} &= \$14,014.50 &&\text{(Cost per Active TB treatment)}\\
  C_{L} &= \$700       &&\text{(Cost per Latent TB treatment)}
\end{align*}
%\begin{enumerate}[1.] \itemsep 0em
%  \item $C_{A}$ = \$14,014.50 (Cost per Active TB treatment)
%  \item $C_{L}$ = \$700 (Cost per Latent TB treatment)
%\end{enumerate}
\vspace{5mm}

@@

To gain insight about strategies to reduce the cost burden for TB in the US, we
focus on the parameters with the greatest PRCC magnitudes for Total Cost aside
from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.  All these
parameters have PRCC magnitudes above 0.7, and are highly correlated with the
total cost burden of TB borne by the US projected over the next 100 years.  Out
of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of
Infection among the US born population in the year 2000, and therefore is
unchangeable under any intervention strategy.  The parameters $p$ (the fraction
of new infections which are acute) and $q$ (the fraction of infections
progressing to infectious disease) are variables which depend on physiological
disease dynamics, and may be altered with advances in medicine or mutations in
the bacterial strains of TB.  The parameter $f$ is the fraction of FB arrivals
with LTBI, which may vary depending on US immigration policies and medical
practices.  These results suggest that treating cases of LTBI among new FB
arrivals may be the most cost efficient intervention strategy to reduce the
disease burden for TB in the US, under the assumptions of the Hill model.  \\
\end{document}
